Supplementary material: The increasing cost of happiness

### 2021-06-24 src/supplementary-SSM1.Rmd
Final resubmission revisions. Closes #20, #17, #4

hilda_data %>%
  filter(year %in% c(2001, 2007, 2013, 2019)) %>%
  filter(!student, !top_hifdip, (!is.na(losat)|!is.na(gh9))) %>%
  mutate(
    `University Graduates` = edu == "Grad",
    ) %>%
  select(
    year, `Household income ($)` = hh_disp_inc_eq,
    `Life satisfaction` = losat, `Happiness` = gh9, 
    Males = male, `Age (years)` = age, `University Graduates`, #Workforce,
    Unemployed = unemployed, Couples = coupled, #`Relationship status`, 
    `Chronic illness` = chronic, SEIFA, 
    `Household size` = hhsize,
  ) %>% 
  tbl_summary(
    by = year,
    missing = "no",
    statistic = 
      list(all_continuous() ~ "{mean} (±{sd})",
           all_categorical() ~ "{n} ({p}%)"),
    digits = 
      list(all_continuous() ~ 1,
           `Household income ($)` ~ 0),
    missing_text = "(Missing)" 
    ) %>%
  add_p(
    test = list(
      all_continuous() ~ "linear_trend_test",
      all_dichotomous() ~ "prop_trend_test"
    )
  ) %>%
  modify_header(stat_by = "{level}\nN = {style_number(n)}") %>%
  as_flex_table() %>%
  align(part = "body") %>%
  valign(valign = "top", part = "header") %>%
  fontsize(size = 9.5, part = "all") %>%
  width(j = 1, width = 1.5) %>%
  width(j = 2:6, width = 1)
```

@@

          },
        .id = "Year") %>%
  mutate(
    Year = str_remove(Year, "fit"),
    Parameter = recode_factor(Parameter, !!!param_key),
    Estimate = if_else(str_detect(Parameter, "Change"),
                       (Estimate * income[Year, "sd"] + income[Year, "mean"])/1000,
                       Estimate),
    Est.Error = if_else(str_detect(Parameter, "Change"),
                        (Est.Error * income[Year, "sd"] + income[Year, "mean"])/1000,
                        Est.Error),
    `l-95% CI` = if_else(str_detect(Parameter, "Change"),
                        (`l-95% CI` * income[Year, "sd"] + income[Year, "mean"])/1000,
                        `l-95% CI`),
    `u-95% CI` = if_else(str_detect(Parameter, "Change"),
                         (`u-95% CI` * income[Year, "sd"] + income[Year, "mean"])/1000,
                         `u-95% CI`)
    ) %>%
  flextable() %>%
  merge_v(j = 1) %>%
  valign(j = 1, valign = "top") %>%
  bg(i = ~Year %in% seq(2001, 2019, 2), 
     bg = "grey90", 
     part = "body") %>%
  colformat_double(j = 3:6, digits= 3) %>%
  colformat_double(j = 7, digits= 1) %>%
  footnote(i = 1, j = 7,
           value = as_paragraph(
             c("Rhat is the potential scale reduction factor on split chains")),
           ref_symbols = c("a"),
           part = "header") %>%
  footnote(i = 1, j = c(8:9),
           value = as_paragraph(
             c("Bulk_ESS and Tail_ESS are effective sample size (ESS) measures")),
           ref_symbols = c("b"),
           part = "header") %>%
  fontsize(size = 9, part = "all") %>%
  width(j = 1, width = .5) %>%
  width(j = 2, width = 1) %>%
  width(j = c(3:7), width = .7) %>%
  width(j = c(8, 9), width = .8)
```

@@

##### Table S3. Bayesian coefficients from linear, log-linear and piecewise-linear models  
```{r table_s3}
map_df(log_fits, .f = ~{
  fixef(.x) %>%
    as_tibble(rownames = "terms") %>%
    transmute(terms, coef = paste0(round(Estimate, 2), " (±", round(Est.Error, 3), ")")) %>%
    spread(terms, coef)},
  .id = "Year"
  ) %>%
  rename("b0_log" = 2, "b1_log" = 3) -> coefs_gh9_log

map_df(lm_fits, .f = ~{
  fixef(.x) %>%
    as_tibble(rownames = "terms") %>%
    transmute(terms, coef = paste0(round(Estimate, 2), " (±", round(Est.Error, 3), ")")) %>%
    spread(terms, coef)},
  .id = "Year"
  ) %>%
  select(Year, "b0_lin" = 3, "b1_lin" = 2) -> coefs_gh9_lm

map_df(nl_fits, .f = ~{
  fixef(.x) %>%
    as_tibble(rownames = "terms") %>%
    transmute(terms, coef = paste0(round(Estimate, 2), " (±", round(Est.Error, 3), ")")) %>%
    spread(terms, coef)},
  .id = "Year"
  ) %>%
  rename("b0_pw" = 2, "b1_pw" = 3, 
         "b2_pw" = 4, "Omega" = 5) -> coefs_gh9_pw

@@

map_df(log_fits_losat, .f = ~{
  fixef(.x) %>%
    as_tibble(rownames = "terms") %>%
    transmute(terms, coef = paste0(round(Estimate, 2), " (±", round(Est.Error, 3), ")")) %>%
    spread(terms, coef)},
  .id = "Year"
) %>%
  rename("b0_log" = 2, "b1_log" = 3) -> coefs_losat_log

map_df(lm_fits_losat, .f = ~{
  fixef(.x) %>%
    as_tibble(rownames = "terms") %>%
    transmute(terms, coef = paste0(round(Estimate, 2), " (±", round(Est.Error, 3), ")")) %>%
    spread(terms, coef)},
  .id = "Year"
) %>%
  select(Year, "b0_lin" = 3, "b1_lin" = 2) -> coefs_losat_lm

map_df(nl_fits_losat, .f = ~{
  fixef(.x) %>%
    as_tibble(rownames = "terms") %>%
    transmute(terms, coef = paste0(round(Estimate, 2), " (±", round(Est.Error, 3), ")")) %>%
    spread(terms, coef)},
  .id = "Year"
) %>%
  rename("b0_pw" = 2, "b1_pw" = 3, 
         "b2_pw" = 4, "Omega" = 5) -> coefs_losat_pw

@@

bind_rows(coefs_affective, coefs_cognitive) %>%
  select(Wellbeing, everything()) %>%
  flextable() %>%
  merge_v(j = 1) %>%
  set_header_labels(values = c(b0_pw = paste0("\u03b2", "0"),
                               b1_pw = paste0("\u03b2", "1"),
                               b2_pw = paste0("\u03b2", "2"),
                               Omega = "\u03C9",
                               b0_log = paste0("\u03b2", "0"),
                               b1_log = paste0("\u03b2", "1"),
                               b0_lin = paste0("\u03b2", "0"),
                               b1_lin = paste0("\u03b2", "1"))) %>%
  add_header(top = TRUE,
             values = c(b0_pw = "Piecewise-linear (±se)",
                        b1_pw = "Piecewise-linear (±se)",
                        b2_pw = "Piecewise-linear (±se)",
                        Omega = "Piecewise-linear (±se)",
                        b0_log = "Log-linear (±se)",
                        b1_log = "Log-linear (±se)",
                        b0_lin = "Linear (±se)",
                        b1_lin = "Linear (±se)")) %>%
  merge_h(part = "header") %>%
  width(j = 1:2, width = c(0.75, 0.5)) %>%
  width(j = 3:10, width = 0.65) %>%
  fontsize(size = 9, part = "all") %>%
  # flextable::theme_vanilla() %>% # theme_vanilla() 
  valign(valign = "top") %>%
  valign(valign = "bottom", part = "header") %>%
  border_remove() %>%
  hline_top(part="header", border = officer::fp_border()) %>%
  hline_bottom(part="header", border = officer::fp_border()) %>%
  hline(i = 19, border = officer::fp_border()) %>%
  hline_bottom(part="body", border = officer::fp_border())
```

@@

##### Table S5. OLS coefficients from linear, log-linear and piecewise models  
```{r table_s5}
lm_coef <- map_dfr(nested_models$lin_fit, broom::tidy, .id = "Year") %>%
  filter(term == "dollars") %>%
  mutate(coefficient = paste0(round(estimate, 3), " (±", round(std.error, 3), ")")) %>%
  select(Year, `linear (±se)` = coefficient)

log_coef <- map_dfr(nested_models$log_fit, broom::tidy, .id = "Year") %>%
  filter(term == "log(dollars)") %>%
  mutate(coefficient = paste0(round(estimate, 3), " (±", round(std.error, 3), ")")) %>%
  select(Year, `log-linear (±se)` = coefficient)

pw_coefs <- map_dfr(nested_models$pw_fit, broom::tidy, .id = "Year") %>%
  filter(term %in% c("dollars", "U1.dollars")) %>%
  select(Year, term, estimate, std.error) %>%
  pivot_wider(id_cols = Year, 
              names_from = term, 
              values_from = estimate:std.error) %>%
  mutate(
    estimate_post = estimate_U1.dollars + estimate_dollars,
    `pre-slope (±se)` = paste0(
      round(estimate_dollars, 3), " ±", round(std.error_dollars, 3)),
    `post-slope (±se)` = paste0(
      round(estimate_post, 3), " ±", round(std.error_U1.dollars, 3))
    ) %>%
  select(Year, `pre-slope (±se)`, `post-slope (±se)`)

pw_coefs <- map_dfr(nested_models$pw_fit, ~as_tibble(.x$psi), .id = "Year") %>%
  mutate(term = "psi.dollars") %>%
  mutate(coefficient = paste0(round(`Est.`, 2)*10, " (±", round(`St.Err`, 2)*10, ")")) %>%
  select(Year, `change point ($000s ±se)` = coefficient) %>%
  left_join(pw_coefs)

>>>>

hilda_data %>%
  filter(year %in% c(2001, 2007, 2013, 2019)) %>%
  filter(!student, !top_hifdip, (!is.na(losat)|!is.na(gh9))) %>%
  mutate(
    `University Graduates` = edu == "Grad",
    ) %>%
  select(
    year, `Household income ($)` = hh_disp_inc_eq,
    `Life satisfaction` = losat, `Happiness` = gh9, 
    Males = male, `Age (years)` = age, `University Graduates`, #Workforce,
    Unemployed = unemployed, Couples = coupled, #`Relationship status`, 
    `Chronic illness` = chronic, SEIFA, 
    `Household size` = hhsize,
  ) %>% 
  tbl_summary(
    by = year,
    missing = "no",
    statistic = 
      list(all_continuous() ~ "{mean} ({sd})",
           all_categorical() ~ "{n} ({p}%)"),
    digits = 
      list(all_continuous() ~ 1,
           `Household income ($)` ~ 0),
    missing_text = "(Missing)" 
    ) %>%
  add_p(
    test = list(
      all_continuous() ~ "linear_trend_test",
      all_dichotomous() ~ "prop_trend_test"
    )
  ) %>%
  modify_header(stat_by = "{level}\nN = {style_number(n)}") %>%
  as_flex_table() %>%
  align(part = "body") %>%
  valign(valign = "top", part = "header") %>%
  fontsize(size = 9.5, part = "all") %>%
  width(j = 1, width = 1.5) %>%
  width(j = 2:5, width = 1.1) %>%
  width(j = 6, width = .6)
```

@@

          },
        .id = "Year") %>%
  mutate(
    Year = str_remove(Year, "fit"),
    Parameter = recode_factor(Parameter, !!!param_key),
    Estimate = if_else(str_detect(Parameter, "Change"),
                       (Estimate * income[Year, "sd"] + income[Year, "mean"])/1000,
                       Estimate),
    Est.Error = if_else(str_detect(Parameter, "Change"),
                        (Est.Error * income[Year, "sd"])/1000,
                        Est.Error),
    `l-95% CI` = if_else(str_detect(Parameter, "Change"),
                        (`l-95% CI` * income[Year, "sd"] + income[Year, "mean"])/1000,
                        `l-95% CI`),
    `u-95% CI` = if_else(str_detect(Parameter, "Change"),
                         (`u-95% CI` * income[Year, "sd"] + income[Year, "mean"])/1000,
                         `u-95% CI`)
    ) %>%
  flextable() %>%
  merge_v(j = 1) %>%
  valign(j = 1, valign = "top") %>%
  bg(i = ~Year %in% seq(2001, 2019, 2), 
     bg = "grey90", 
     part = "body") %>%
  colformat_double(j = 3:6, digits= 3) %>%
  colformat_double(j = 7, digits= 1) %>%
  footnote(i = 1, j = 7,
           value = as_paragraph(
             c("Rhat is the potential scale reduction factor on split chains")),
           ref_symbols = c("a"),
           part = "header") %>%
  footnote(i = 1, j = c(8:9),
           value = as_paragraph(
             c("Bulk_ESS and Tail_ESS are effective sample size (ESS) measures")),
           ref_symbols = c("b"),
           part = "header") %>%
  fontsize(size = 9, part = "all") %>%
  width(j = 1, width = .5) %>%
  width(j = 2, width = 1) %>%
  width(j = c(3:7), width = .7) %>%
  width(j = c(8, 9), width = .8)
```

@@

##### Table S3. Bayesian coefficients from linear, log-linear and piecewise-linear models  
```{r table_s3}
map_df(log_fits, .f = ~{
  fixef(.x) %>%
    as_tibble(rownames = "terms") %>%
    transmute(terms, coef = paste0(round(Estimate, 2), " (", round(Est.Error, 3), ")")) %>%
    spread(terms, coef)},
  .id = "Year"
  ) %>%
  rename("b0_log" = 2, "b1_log" = 3) -> coefs_gh9_log

map_df(lm_fits, .f = ~{
  fixef(.x) %>%
    as_tibble(rownames = "terms") %>%
    transmute(terms, coef = paste0(round(Estimate, 2), " (", round(Est.Error, 3), ")")) %>%
    spread(terms, coef)},
  .id = "Year"
  ) %>%
  select(Year, "b0_lin" = 3, "b1_lin" = 2) -> coefs_gh9_lm

map_df(nl_fits, .f = ~{
  fixef(.x) %>%
    as_tibble(rownames = "terms") %>%
    transmute(terms, coef = paste0(round(Estimate, 2), " (", round(Est.Error, 3), ")")) %>%
    spread(terms, coef)},
  .id = "Year"
  ) %>%
  rename("b0_pw" = 2, "b1_pw" = 3, 
         "b2_pw" = 4, "Omega" = 5) -> coefs_gh9_pw

@@

map_df(log_fits_losat, .f = ~{
  fixef(.x) %>%
    as_tibble(rownames = "terms") %>%
    transmute(terms, coef = paste0(round(Estimate, 2), " (", round(Est.Error, 3), ")")) %>%
    spread(terms, coef)},
  .id = "Year"
) %>%
  rename("b0_log" = 2, "b1_log" = 3) -> coefs_losat_log

map_df(lm_fits_losat, .f = ~{
  fixef(.x) %>%
    as_tibble(rownames = "terms") %>%
    transmute(terms, coef = paste0(round(Estimate, 2), " (", round(Est.Error, 3), ")")) %>%
    spread(terms, coef)},
  .id = "Year"
) %>%
  select(Year, "b0_lin" = 3, "b1_lin" = 2) -> coefs_losat_lm

map_df(nl_fits_losat, .f = ~{
  fixef(.x) %>%
    as_tibble(rownames = "terms") %>%
    transmute(terms, coef = paste0(round(Estimate, 2), " (", round(Est.Error, 3), ")")) %>%
    spread(terms, coef)},
  .id = "Year"
) %>%
  rename("b0_pw" = 2, "b1_pw" = 3, 
         "b2_pw" = 4, "Omega" = 5) -> coefs_losat_pw

@@

bind_rows(coefs_affective, coefs_cognitive) %>%
  select(Wellbeing, everything()) %>%
  flextable() %>%
  merge_v(j = 1) %>%
  set_header_labels(values = c(b0_pw = paste0("\u03b2", "0"),
                               b1_pw = paste0("\u03b2", "1"),
                               b2_pw = paste0("\u03b2", "2"),
                               Omega = "\u03C9",
                               b0_log = paste0("\u03b2", "0"),
                               b1_log = paste0("\u03b2", "1"),
                               b0_lin = paste0("\u03b2", "0"),
                               b1_lin = paste0("\u03b2", "1"))) %>%
  add_header(top = TRUE,
             values = c(b0_pw = "Piecewise-linear (se)",
                        b1_pw = "Piecewise-linear (se)",
                        b2_pw = "Piecewise-linear (se)",
                        Omega = "Piecewise-linear (se)",
                        b0_log = "Log-linear (se)",
                        b1_log = "Log-linear (se)",
                        b0_lin = "Linear (se)",
                        b1_lin = "Linear (se)")) %>%
  merge_h(part = "header") %>%
  width(j = 1:2, width = c(0.75, 0.5)) %>%
  width(j = 3:10, width = 0.65) %>%
  fontsize(size = 9, part = "all") %>%
  # flextable::theme_vanilla() %>% # theme_vanilla() 
  valign(valign = "top") %>%
  valign(valign = "bottom", part = "header") %>%
  border_remove() %>%
  hline_top(part="header", border = officer::fp_border()) %>%
  hline_bottom(part="header", border = officer::fp_border()) %>%
  hline(i = 19, border = officer::fp_border()) %>%
  hline_bottom(part="body", border = officer::fp_border())
```

@@

##### Table S5. OLS coefficients from linear, log-linear and piecewise models  
```{r table_s5}
lm_coef <- map_dfr(nested_models$lin_fit, broom::tidy, .id = "Year") %>%
  filter(term == "dollars") %>%
  mutate(coefficient = paste0(round(estimate, 3), " (", round(std.error, 3), ")")) %>%
  select(Year, `linear (se)` = coefficient)

log_coef <- map_dfr(nested_models$log_fit, broom::tidy, .id = "Year") %>%
  filter(term == "log(dollars)") %>%
  mutate(coefficient = paste0(round(estimate, 3), " (", round(std.error, 3), ")")) %>%
  select(Year, `log-linear (se)` = coefficient)

pw_coefs <- map_dfr(nested_models$pw_fit, broom::tidy, .id = "Year") %>%
  filter(term %in% c("dollars", "U1.dollars")) %>%
  select(Year, term, estimate, std.error) %>%
  pivot_wider(id_cols = Year, 
              names_from = term, 
              values_from = estimate:std.error) %>%
  mutate(
    estimate_post = estimate_U1.dollars + estimate_dollars,
    `pre-slope (se)` = paste0(
      round(estimate_dollars, 3), " ±", round(std.error_dollars, 3)),
    `post-slope (se)` = paste0(
      round(estimate_post, 3), " ±", round(std.error_U1.dollars, 3))
    ) %>%
  select(Year, `pre-slope (se)`, `post-slope (se)`)

pw_coefs <- map_dfr(nested_models$pw_fit, ~as_tibble(.x$psi), .id = "Year") %>%
  mutate(term = "psi.dollars") %>%
  mutate(coefficient = paste0(round(`Est.`, 2)*10, " (", round(`St.Err`, 2)*10, ")")) %>%
  select(Year, `change point ($000s ±se)` = coefficient) %>%
  left_join(pw_coefs)
